\begin{center}
	\textbf{\Huge Henrique Miossi de Araújo} \\ \vspace{5pt}
	\small \faPhone* \texttt{+55 (27)99248-7726} \hspace{1pt} $•$
	\hspace{1pt} \faEnvelope \hspace{2pt} \texttt{henriquemiossi@gmail.com} \hspace{1pt}
	% \hspace{1pt} \faYoutube \hspace{2pt} \texttt{harshibar} \hspace{1pt} $|$
	% \hspace{1pt} \faMapMarker* \hspace{2pt}\texttt{Vila Velha, ES, Brasil}
	\\ \hspace{1pt} \faLinkedin \hspace{2pt} \texttt{https://www.linkedin.com/in/henriquemiossidearaujo/} $•$
	\hspace{1pt} \faGithub \hspace{2pt} \texttt{https://github.com/HenriqueMiossi}
	\\ \vspace{-3pt}
\end{center}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
\resumeSubHeadingListStart

\resumeSubheading
{Sisecom Sistemas}{Jul. 2022 -- Jul. 2023}
{Fullstack Development Intern}{}
\resumeItemListStart
\resumeItem{I modernized a complete kart track administration desktop solution with Windows Forms and .NET MAUI, including an interface redesign;}
\resumeItem{I developed an Android and iOS mobile application with .NET MAUI, working on prototyping the user experience and developing specific solutions for each platform needs, using native frameworks and the Android NDK;}
\resumeItem{I worked with all web components of the systems, including the creation of REST APIs, the use of Websockets in real-time components and the development of web pages focused on emails;}
\resumeItem{System solution used by dozens of companies in the sector around Brazil;}
\resumeItemListEnd

\resumeSubheading
{Evoke Games}{Dec. 2021 -- Apr. 2022}
{Fullstack Developer}{}
\resumeItemListStart
\resumeItem{I developed a REST API in TypeScript hosted on AWS Lambda to manage the inner workings of a DeFi game, including carrying out transactions on the Ethereum and BNB Smart Chain blockchains;}
\resumeItem{I maintained several websites built in ReactJS and JavaScript;}
\resumeItem{Project with thousands of users on Telegram and Discord;}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section {EDUCATION AND CERTIFICATIONS}
\resumeSubHeadingListStart

\resumeSubheading
{Vila Velha University}{Jan. 2020 -- Dec. 2023}
{Bachelor's Degree in Information Systems}
{Vila Velha, ES, Brazil}
\resumeSubHeadingListEnd

\resumeSubHeadingListStart

\vspace{-1pt}\item
\begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
	\textbf{Cisco Networking Academy} & {\color{dark-grey}\small}\vspace{1pt}\\ % top row of resume entry
	\textit{CCNAv7: Introduction to Networks Certificate} & {\color{dark-grey} \small Jun. 2022}\\ % second row of resume entry
	\textit{Cybersecurity Essentials Certificate} & {\color{dark-grey} \small Mar. 2022}\\ % second row of resume entry
	\textit{IT Essentials: PC Hardware and Software Certificate} & {\color{dark-grey} \small Jun. 2020}\\ % second row of resume entry
\end{tabular*}\vspace{-4pt}

\resumeSubHeadingListEnd
%-------PROJECTS AND REALIZATIONS--------
\section{PROJECTS AND ACHIEVEMENTS}
\resumeSubHeadingListStart
\resumeSubheading
{Voluntary Scientific Initiation - Vila Velha University}{Jul. 2022 -- Jul. 2023}
{NER em Acórdãos da TNU: Pedidos de Uniformização}{}

\resumeSubheading
{ICPC - International Collegiate Programming Contest}{Nov. 2020}
{XXVI Programming Marathon}{}
          
\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
\begin{itemize}[leftmargin=0in, label={}]
	\small{\item{
		\textbf{Programming Languages:}
		{HTML, CSS, JavaScript, TypeScript, Python, C\#, C++}
		\vspace{2pt} \\
				
		\textbf{Technologies:}
		{Git, NodeJS, PostgreSQL, SQL Server, MongoDB, ReactJS, React Native, .NET Core, .NET MAUI, Windows Forms, Docker}
		\vspace{2pt} \\
						     
		\textbf{Tools and Platforms:}
		{GitHub, GitLab, Figma, Adobe Photoshop, Windows, Linux}
		\vspace{2pt} \\
						     
		\textbf{Languages:}
		{Native Portuguese, Advanced English, Basic Spanish}
	}}
\end{itemize}